Stack Safety as a Security Property

### 2021-03-07 main.tex
Fixed up some broken proofs in ObsTrace.v

\begin{enumerate}
\item \(\MPCT\) may be finite and \(\pi_\context(\last(\MPCT)) = (\_,\depth')\) with \(\depth' < \depth\),
  and \(\pi_\context(\last(\NPCT)) = (\_,\depth')\) with \(\depth' < \depth\). That is, both traces end
  having left the call of depth \(\depth\). Further:
  \begin{itemize}
  \item They have the same observable behavior, \(\pi_\obs(\MPCT) \simeq \pi_\obs(\NPCT)\)
  \item Their final states have the same differences, \(\pi_\mach(\head(\MPCT)), \pi_\mach(\last(\MPCT)) \diamond
  \pi_\mach(\head(\MPCT)), \pi_\mach(\last(\NPCT))\)
  \end{itemize}
\item \(\MPCT\) and \(\NPCT\) may both be infinite, with \(\pi_\obs(\MPCT) \simeq \pi_\obs(\NPCT)\)
\item \(\MPCT\) may be finite but end without returning -- which can only have happened if it fail-stopped --
  and its observable behavior prefixes that of \(\NPCT\), \(\pi_\obs(\MPCT) \lesssim \pi_\obs(\NPCT)\)
\item \(\NPCT\) may end with a fail-stop as in case 3, with \(\pi_\obs(\NPCT) \lesssim \pi_\obs(\MPCT)\)
\end{enumerate}

@@

\subsection{Coroutine Safety}
\[\ann \in \ANNS ::= \powerset(\{\callmap, \retmap, \yieldmap\} \cup
\{\sharemap ~ P | P \subseteq \MACHS \times \COMPONENTS \} \cup
\{\passmap ~ P | P \subseteq \MACHS \times \COMPONENTS \})\]

>>>>

\begin{enumerate}
\item \(\MPCT\) may be finite and \(\pi_\context(\last(\MPCT)) = (\_,\depth')\) with \(\depth' < \depth\),
  and \(\pi_\context(\last(\NPCT)) = (\_,\depth')\) with \(\depth' < \depth\). That is, both traces end
  having left the call of depth \(\depth\). Further:
  \begin{itemize}
  \item They have the same observable behavior, \(\pi_\obs(\MPCT) \simeq \pi_\obs(\NPCT)\)
  \item Their final states have the same differences:
    \[\pi_\mach(\head(\MPCT)), \pi_\mach(\last(\MPCT)) \diamond
    \pi_\mach(\head(\MPCT)), \pi_\mach(\last(\NPCT))\]
  \end{itemize}
\item \(\MPCT\) and \(\NPCT\) may both be infinite, with \(\pi_\obs(\MPCT) \simeq \pi_\obs(\NPCT)\)
\item \(\MPCT\) may be finite but end without returning -- which can only have happened if it fail-stopped --
  and its observable behavior prefixes that of \(\NPCT\), \(\pi_\obs(\MPCT) \lesssim \pi_\obs(\NPCT)\)
\item \(\NPCT\) may end with a fail-stop as in case 3, with \(\pi_\obs(\NPCT) \lesssim \pi_\obs(\MPCT)\)
\end{enumerate}

@@

\subsection{Coroutine Safety}

Our final extension to the model is to add coroutines. We assume a very simple model with
a fixed number of coroutines, each with its own stack.
Stack identifiers are drawn from a set \(\STACKS\), and there is a static partial map
\(\stackof\) from addresses to stack ids. The ``active stack'' -- the stack belonging to the
currently executing coroutine -- in any given machine state is \(\stackof(\mach ~ \SP)\).
We extend the set of possible annotations with a yield.

\[\ann \in \ANNS ::= \callmap + \retmap + \yieldmap +
\sharemap(P \subseteq \MACHS \times \COMPONENTS) +
\passmap(P \subseteq \MACHS \times \COMPONENTS)\]

We use the same domain model as above, but instead of keeping track of a single depth
we use a map from stacks to their depths.

\[\context \in \CONTEXTS ::= (\domMap \in \COMPONENTS \rightarrow \STKDOMS) \times
(\depthMap \in \STACKS \rightarrow \mathbb{N})\]
